---
title: "STAT 345 Final Project - Real Estate"
author: "STAT 345"
output: html_document
---

Expected Submission: You will generate a well-written R Markdown report that addresses the following prompts. This R Markdown report should source your analysis code and only display top-level, abstracted code _if/when appropriate_. Choices made during the analysis project should be described and justified in the report. You will present on your results during the final exam period for the semester. The written report (knitted file), presentation file, and your analysis code should be submitted to D2L by Tuesday, May 14 at 12:15pm. 

**General advice:** Get started early. If you wait to the last minute, it will not go well. For this project, you may find yourself spending a reasonable amount of time _searching_ for help.

1. _Rules!_ Monopoly has several rules related to movement around the game board. Movement is affected by standard dice rolls, special conditions for some dice rolls, and game cards. Find and summarize these rules. 

2. _Let's Get Moving_ Build a system that allows for up to 4 players to move around the game board. As a first attempt, focus on standard dice rolls, ignoring additional rules related to rolling doubles, jail, or special cards. Which properties are landed on most frequently? Create a visualization for this!

3. _Double Down_ Improve your system to incorporate going to jail, including the doubles-rolling condition. Which properties are landed on most frequently now? Has this changed dramatically from the previous system (that didn't account for jail)? Again, visualize this!

4. _Take a Chance_ Incorporate the movement cards into your system. You can ignore the effects of non-movement cards, but not their existence! Which properties are landed on most frequently now? Has this changed dramatically from the previous system (that didn't account for Chance)? Again, visualize this!

5. _Play a Game_ Extend your system to allow for up to 4 players to "play" the game. You may choose a reasonable starting board and player money level (so, you don't have to buy properties). Include payments between players, payments to the bank, and payments from the bank (there are several cards that will effect these that you should account for). You do not need to consider mortgaging properties (so a player loses when their liquid cash has run out). How long do games typically last given your starting board and money level? How does this change if money paid to the bank is placed in "Free Parking" and awarded to players landing on that space?


```{r}
#prop <- read.csv("Properties.csv")
prop <- read.csv("Game_Board_Spaces_Git.csv")
equip <- read.csv("General Equipment CSV.csv")
players <- read.csv("Players Dataset CSV.csv")
railroads <- read.csv("Railroads Dataset CSV.csv")
deeds <- read.csv("Title Deeds Dataset CSV.csv")
util <- read.csv("Utilities Dataset CSV.csv")
action_cards <- read.csv("Action_Cards_Git.csv")

#make dataframes more tidy:
library(tidyverse)
deeds <- deeds %>% select(-"Identifier")
util <- util %>% select("Utility.Company", "Purchase.Price", "Rent.with.1.Utility", "Rent.with.2.Utility", "Mortgage.Value")
action_cards <- action_cards %>% select(-Money)

#install.packages("devtools")
#devtools::install_github("mkuhn/dict")
library(dict)

players <- c(1,2,3,4)
position <- dict()
position[1] <- 1
position[2] <- 1
position[3] <- 1
position[4] <- 1

spaces <- dict()
locations <- c(prop$Properties)
i <- 0
while(i < 41){
  spaces[i] <- locations[i]
  i <- i + 1
}

```


#creating and initiating board:
```{r}
board <- vector(mode = "list", length = 40)

#sets each board space to count 0
for( i in 1:40){
  board[[i]] <- 0
}
```

#counting amount of times a space is landed on:
```{r}
position[1] <- 1
num <- position[[1]]

simulation <- function(times){
  
  for(i in 1:times){
position[1] <-rollDice(0,1)
num <- position[[1]]
board[[num]] <- board[[num]] + 1
  }
}
```
#frequency simulation and graph
```{r}
library(tidyverse)

spot_frequency <- simulation(5)

frequency_data <- as.data.frame(spot_frequency) 

frequency_data <- frequency_data %>% pivot_longer(1:40)

frequency_data
ggplot(frequency_data, aes(1:40, value)) + geom_col()
```

```{r}
#more complex dice roll that factors in double rolls
  dice_roll <- function(){
  
  #first dice roll 
  dice <- sample(1:6, 2, replace = TRUE)
  
  #if you roll doubles, rolls again
  if(dice[1] == dice[2]){
    
    dice <- sample(1:6, 2, replace = TRUE)
    
    #if you roll doubles, rolls again
    if(dice[1] == dice[2]){
    
      dice <- sample(1:6, 2, replace = TRUE)
      
      #if you roll doubles, tells you to go to jail
      if(dice[1] == dice[2]){
    
      dice <- sample(1:6, 2, replace = TRUE)
      print("Go to Jail")
     }
    }
  }
  
  #prints the sum of your numbers (amount of spots you move) unless you go to jail
  if(dice[1] != dice[2]){
  
    sum(dice)
  }
}
```

#chance card: finding the neareset railraod
```{r}
railroad_num <- c(6, 15, 25, 35)

position[1] <- 40
position[[1]]

difference <- railroad_num - position[[1]]
difference

maxnegative <- function(x){
  min(x)
}
minpositive <- function(x){
  min(x[x > 0])
}

if (all(difference < 0)){
   print("All values are non-negatives!")
  distance <- maxnegative(difference)
  
}else{
  distance <- minpositive(difference)
}

distance

next_railraod <- distance + position[[1]]

position[1] <- next_railraod

position[[1]]
```

#UPDATED IDEAS: JAIL (05-02-2021)
  #New Jail Idea; better jail function

#Check Player's Hand:
```{r}
Check_Hand <- function(player_identifier)
{
  Players_Hands_Dataset[player_identifier,]
}
```

#Old Go to Jail:
```{r}
#unsure how we want to create a jail; idea is that we can have at most four players in jail at once, so we can assign each element of a list of cardinality 4 a unique position which corresponds to the player's number.

jail <- list(NA, NA, NA, NA)

Old_Go_to_Jail <- function(playerID)
{
  jail[[playerID]] <- playerID
  return(jail)
}
```

#Go to Jail:
```{r}
#unsure how we want to create a jail; idea is that we can have at most four players in jail at once, so we can assign each element of a list of cardinality 4 a unique position which corresponds to the player's number.

Go_to_Jail <- function(playerID)
{
  position[[playerID]] <- 11
  user_place <- position[[playerID]]
  
  return(user_place)
}
```

#In Jail/Exiting Jail:
```{r}
#Needs additional work to count how long someone has been in jail for.
#Currently works for all cases, but there is an issue updating the location of the player upon exiting jail. (Maybe not an issue, as we only care about their first roll upon exiting...issue appears with multiple iterations)
#Issue fied by fixing position of player i = 11. 

In_Out_Jail <- function(player_identifer, counter = 0)
{
  position[player_identifer] <- 11
  
  hand <- Check_Hand(player_identifer)
  card <- hand %>% select(Get.Out.of.Jail.Free) 
  
  if(is.na(card) == FALSE)
  {
    players[player_identifer, ]$Get.Out.of.Jail.Free <- NA
    print(paste0("Player", player_identifer, " uses a 'Get Out of Jail Free Card.'"))
    roll_to_move_player(playerID = player_identifer, player_position = 11)
  }
  
  else
  {
    funds <- hand %>% select(Bank)
    
    if(funds >= 500)
    {
      players[player_identifer, ]$Bank <- players[player_identifer, ]$Bank - 50
      print(paste0("Player", player_identifer, " pays M$ 50 to exit jail."))
      roll_to_move_player(playerID = player_identifer, player_position = 11)
    }
    
    else
    {
      roll <- roll_dice()
      
      if(roll[1] == roll[2])
      { 
        print(paste0("Player", player_identifer, " rolls doubles to exit jail."))
        roll_to_move_player(playerID = player_identifer, player_position = 11)
      }
      
      else
      {
        if(counter < 2)
        {
          print(paste0("Player", player_identifer, " remains in jail."))
          In_Out_Jail(player_identifer, counter + 1)
        }
        
        else
        {
          funds <- hand %>% select(Bank)
    
          if(funds >= 50)
          {
            funds[[1]] <- funds[[1]] - 50
            
            print(paste0("Player", player_identifer, " pays M$ 50 to exit jail."))
            roll_to_move_player(playerID = player_identifer, player_position = 11)
          }
          
          else
          {
            print(paste0("Player", player_identifer, " is bankrupted."))
            #remove player from player dataset?
          }
        }
      }
    }
  }
  
  invisible(players)
}
```

#NEW COMMIT (04-29-2021)
  #Note: Movement was tested with a list instead of a dictonary, as the install for the library(dict) kept erroring out on my computer; there did not appear to be any significant changes in the structure of the code however, and it is therefore my belief the function will work for the dictonary too. (I can share the code for the list later if that is needed.)

#Simple Roll Dice:
```{r}
roll_dice <- function()
{
  dice <- sample(1:6, 2, replace = TRUE)
  return(dice)
}
```   

#Force Doubles / Force Differing Dice
```{r}
force_doubles <- function()
{
  dice <- sample(1:1, 2, replace = TRUE)
  return(dice)
}

differing_dice <- function()
{
  dice <- sample(1:6, 2, replace = TRUE)
  
  while (dice[1] == dice[2]) 
  {
    dice <- sample(1:6, 2, replace = TRUE)
  }
  
  return(dice)
}
```

#Moving Functions:
```{r}
moving <- function(playerID, spaces_to_move)
{
  #Player's position on board + dice roll amount:
  position[[playerID]] <- position[[playerID]] + spaces_to_move
  user_place <- position[[playerID]]
  
  #Restarts Count after Passing GO:
  if(user_place >= 41)
  {
    user_place <- user_place - 40
  }
  
  print(paste0("Player", playerID, " moves ", spaces_to_move, " spaces and lands on: ", spaces[[user_place]]))
  #position[playerID] <- user_place
  return(user_place)
}
```

```{r}
moving_doubles <- function(playerID, spaces_to_move, player_location)
{
  position[[playerID]] <- player_location
  position[[playerID]] <- position[[playerID]] + spaces_to_move
  user_place <- position[[playerID]]
  
  #Restarts Count after Passing GO:
  if(user_place >= 41)
  {
    user_place <- user_place - 40
  }
  
  print(paste0("Player", playerID, " moves ", spaces_to_move, " spaces and lands on: ", spaces[[user_place]]))
  #position[playerID] <- user_place
  return(user_place)
}
```

#Rolls for Movement:
```{r}
#The following function rolls the dice for movement purposes; there are a couple parts worth noting:
  #The roll_to_move_player function uses three functions: roll_dice, moving, and moving_doubles
  #There are several cases to consider, but they are all designed to account for the count of the doubles and player location after each movement. 
  #The moving function and moving doubles function can likely be combined by adding a count argument and using an if/else statement to update player location based on the presence of doubles.

roll_to_move_player <- function(playerID, counter = 0, player_position = 1)
{
  #print(player_position)
  p <- player_position
  #print(p)
  
  
  roll <- roll_dice()
  #roll <- force_doubles()
  #roll <- differing_dice()
  #roll <- c(3, 4)
  
  if(roll[1] == roll[2])
  {
    if(counter == 2)
    {
      print(paste0("Player", playerID, " is sent to Jail for rolling too many doubles.", " The sum of their roll is: ", totalDice))
      #moving()
      return()
    }
    
    else
    {
      print(counter)
      totalDice <- sum(roll)
  
      if(counter == 0 || counter == 1)
      {
        print(paste0("Player", playerID, " rolls doubles!", " The sum of their roll is: ", totalDice))
        new_position <- moving(playerID, totalDice)
        player_position <- new_position
        #print(player_position)
      }
      
      else
      {
        print(paste0("Player", playerID, " rolls again and rolls: ", totalDice))
        new_position <- moving_doubles(playerID, totalDice, p)
        player_position <- new_position
        #print(player_position)
      }
    
      
      roll_to_move_player(playerID, counter + 1, new_position)
    }
  }
  
  else
  {
    totalDice <- sum(roll)
    if(counter == 0)
    {
      print(paste0("Player", playerID, " rolls: ", totalDice))
      moving(playerID, totalDice)
    }
    
    else
    {
      print(paste0("Player", playerID, " rolls again and rolls: ", totalDice))
      moving_doubles(playerID, totalDice, p)
    }
    
  }
}
```

#Move Player 1 for Testing:
```{r}
position[1]
position[1] <- roll_to_move_player(1)
position[1]

#position[1] <- 1

```
