---
title: "STAT 345 Final Project - Real Estate"
author: "STAT 345"
output: html_document
---

Expected Submission: You will generate a well-written R Markdown report that addresses the following prompts. This R Markdown report should source your analysis code and only display top-level, abstracted code _if/when appropriate_. Choices made during the analysis project should be described and justified in the report. You will present on your results during the final exam period for the semester. The written report (knitted file), presentation file, and your analysis code should be submitted to D2L by Tuesday, May 14 at 12:15pm. 

**General advice:** Get started early. If you wait to the last minute, it will not go well. For this project, you may find yourself spending a reasonable amount of time _searching_ for help.

1. _Rules!_ Monopoly has several rules related to movement around the game board. Movement is affected by standard dice rolls, special conditions for some dice rolls, and game cards. Find and summarize these rules. 

2. _Let's Get Moving_ Build a system that allows for up to 4 players to move around the game board. As a first attempt, focus on standard dice rolls, ignoring additional rules related to rolling doubles, jail, or special cards. Which properties are landed on most frequently? Create a visualization for this!

3. _Double Down_ Improve your system to incorporate going to jail, including the doubles-rolling condition. Which properties are landed on most frequently now? Has this changed dramatically from the previous system (that didn't account for jail)? Again, visualize this!

4. _Take a Chance_ Incorporate the movement cards into your system. You can ignore the effects of non-movement cards, but not their existence! Which properties are landed on most frequently now? Has this changed dramatically from the previous system (that didn't account for Chance)? Again, visualize this!

5. _Play a Game_ Extend your system to allow for up to 4 players to "play" the game. You may choose a reasonable starting board and player money level (so, you don't have to buy properties). Include payments between players, payments to the bank, and payments from the bank (there are several cards that will effect these that you should account for). You do not need to consider mortgaging properties (so a player loses when their liquid cash has run out). How long do games typically last given your starting board and money level? How does this change if money paid to the bank is placed in "Free Parking" and awarded to players landing on that space?


```{r}
prop <- read.csv("Properties.csv")
equip <- read.csv("General Equipment CSV.csv")
players <- read.csv("Players Dataset CSV.csv")
railroads <- read.csv("Railroads Dataset CSV.csv")
deeds <- read.csv("Title Deeds Dataset CSV.csv")
util <- read.csv("Utilities Dataset CSV.csv")

#install.packages("devtools")
#devtools::install_github("mkuhn/dict")
library(dict)

players <- c(1,2,3,4)
position <- dict()
position[1] <- 1
position[2] <- 1
position[3] <- 1
position[4] <- 1
board <- vector(mode = "list", length = 40)


spaces <- dict()
locations <- c(prop$Properties)
i <- 0
while(i < 40){
  spaces[i] <- locations[i]
  i <- i + 1
}


```

```{r}
rollDice <- function(counter = 0, playerID){
  diceOne <- sample(1:6, 1)
  diceTwo <- sample(1:6, 1)
  diceOne
  diceTwo
  if(diceOne == diceTwo){
    if(counter == 2){
      print("Go to Jail")
      #moving()
      return()
    }
    totalDice <- diceOne + diceTwo
    moving(playerID, totalDice)
    rollDice(counter + 1, playerID)
  }
  else{
    totalDice <- diceOne + diceTwo
    moving(playerID, totalDice)
  }
}


moving <- function(playerNum, space){
  
  #place you were previously at and the amount you move
  position[[playerNum]] <- position[[playerNum]] + space
  user_place <- position[[playerNum]]
  print("you traveled this many squares")
  print(space)
  #if you get to the last square, it will restart 
   if(position[[playerNum]] > 41){
    position[[playerNum]] <- position[[playerNum]] - 40
  }

  print("You landed on")
  print(spaces[[user_place]])
  position[playerNum] <- user_place
  print(position[1])
  return(user_place)
}


position[1] <- rollDice(0,1)
position[1]
```


```{r}
#more complex dice roll that factors in double rolls
  dice_roll <- function(){
  
  #first dice roll 
  dice <- sample(1:6, 2, replace = TRUE)
  
  #if you roll doubles, rolls again
  if(dice[1] == dice[2]){
    
    dice <- sample(1:6, 2, replace = TRUE)
    
    #if you roll doubles, rolls again
    if(dice[1] == dice[2]){
    
      dice <- sample(1:6, 2, replace = TRUE)
      
      #if you roll doubles, tells you to go to jail
      if(dice[1] == dice[2]){
    
      dice <- sample(1:6, 2, replace = TRUE)
      print("Go to Jail")
     }
    }
  }
  
  #prints the sum of your numbers (amount of spots you move) unless you go to jail
  if(dice[1] != dice[2]){
  
    sum(dice)
  }
}
```
#NEW IDEAS (04-26-2021)
   #FUNCTIONS: Combined previous dice roll ideas; Check Hand; Go to Jail; In Jail/Exiting Jail
   #CONSIDERATIONS: I think a simple dice roll function that can be applied to more complex situations might be useful; explained in greater detail below.

#Simple Roll Dice:
```{r}
new_roll_dice <- function(){
  dice <- sample(1:6, 2, replace = TRUE)
  return(dice)
}
new_roll_dice()
```   

#Check Player's Hand:
```{r}
Check_Hand <- function(player_identifier)
{
  Players_Hands_Dataset[player_identifier,]
}
```

#Go to Jail:
```{r}
#unsure how we want to create a jail; idea is that we can have at most four players in jail at once, so we can assign each element of a list of cardinality 4 a unique position which corresponds to the player's number.

jail <- list(NA, NA, NA, NA)

Go_to_Jail <- function(player_identifier)
{
  jail[[player_identifier]] <- player_identifier
  jail
  #end turn
}
```

#In Jail/Exiting Jail:
```{r}
#Needs additional work to count how long someone has been in jail for. 

In_Out_Jail <- function(player_identifer)
{
  hand <- Check_Hand(player_identifer)
  card <- hand %>% select(Get.Out.of.Jail.Free) 
  
  if(is.na(card) == FALSE)
  {
    card[[1]] <-NA
    print(paste0("Player", player_identifer, " uses a 'Get Out of Jail Free Card.'"))
    #return player to just visiting
    #initiate new roll
  }
  
  else
  {
    funds <- hand %>% select(Bank)
    
    if(funds >= 500)
    {
      funds[[1]] <- funds[[1]] - 50
      
      print(paste0("Player", player_identifer, " pays M$ 50 to exit jail."))
      #return player to just visiting
      #initiate new roll
    }
    
    else
    {
      roll <- new_roll_dice()
      
      if(roll[1] == roll[2])
      { 
        print(paste0("Player", player_identifer, " rolls doubles to exit jail."))
        #return player to just visiting
        #initiate new roll
      }
      
      else
      {
        print(paste0("Player", player_identifer, " remains in jail."))
        Go_to_Jail(player_identifer)
      }
    }
    
  }
}
```


